Democratizing Secure Two-Party Computation

### 2017-10-13 OaklandSubmission/intro.tex
related

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community. \nc{Why do we call it SMC? A bit non-standard for crypto audiences isnt it?} \divya{I drank my tears and a part of me died when I did this. Apparently thats what it is called outside the theory community.}

@@

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} \divya{Bullet list would look bad. I tried listing both options first and then discussing but its hard to talk about ABY before.} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers. 
\nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.}
Now the third option is to hire a cryptographer to design specialised protocols for the functionalities. 
In our work, we achieve the best of all options. \divya{add a word like automatically..}
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targeting when we show our comparisons and we say that we beat or match hand-crafted protocols} \divya{We can do this! Might have to see the flow.}

@@

\tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

Our compiler is aware of cryptographic costs of different representations and inter-conversions.  Based on these costs, our compiler, given a program in \tool, automatically picks Arithmetic and Boolean representations for different sub-parts of the program and inserts the required inter-conversions as well. 
Our experiments show that automatically generated protocols using \tool match the performance of tailor-made protocols in \cite{minionn,shafindss} (see \sectionref{eval}). This shows that  \tool achieves generality, performance and programmer productivity. These features allow us to evaluate our system on a variety of benchmarks, especially, state-of-the-art ML prediction algorithms with \emph{real} data and models.

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or something to outline the different contributions? Above feels like one big story.}

Another issue in adoption of SMC is difficulty in scaling to large programs. 
%In general, SMC implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all SMC implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine. \nc{Should we point out here that ABY itself has an explicit limit on circuit size and also give an example of a program that easily surpasses this bound? Also, hadnt ABY also said something about this? If so, we can mention this.}
To address this issue, we develop a technique called \emph{pipelining} that allows us to run aribitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of pipelining and prove the correctness and security of this transformation in \sectionref{pipe}.

Finally, our framework \tool can serve as a meaningful baseline for future works on hand-crafted SMC protocols for specific functionalities such as \textsc{MiniONN} \cite{minionn}. 
Prior to our work, garbled circuit based two-party computation is cited as the most practical approach and used as the baseline for comparison of performance. But, it has been observed multiple times this approach does not even scale on realistic examples.

@@

\noindent\textbf{Related Work} \divya{I think we should say a few words here about the following: minionn, verilog paper, 
\cite{lambdaps,wysteria}

>>>>

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community.

@@

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options.  
\begin{tiret}
\item He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers.

\item Now the third option is to hire a cryptographer to design specialised protocols for the functionalities. 
\end{tiret}
In our work, we achieve the best of all options.

@@

\textbf{Programmability.} \tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

\textbf{Performance.} Our compiler is aware of cryptographic costs of different representations and inter-conversions.  Based on these costs, our compiler, given a program in \tool, automatically picks Arithmetic and Boolean representations for different sub-parts of the program and inserts the required inter-conversions as well. 
Our experiments show that automatically generated protocols using \tool match the performance of tailor-made protocols in \cite{minionn,shafindss} (see \sectionref{eval}). This shows that  \tool achieves generality, performance and programmer productivity. These features allow us to evaluate our system on a variety of benchmarks, especially, state-of-the-art ML prediction algorithms with \emph{real} data and models.

\textbf{Type system.} We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or something to outline the different contributions? Above feels like one big story.}

\textbf{Pipelining.} Another issue in adoption of SMC is difficulty in scaling to large programs. 
%In general, SMC implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all SMC implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine. \nc{Should we point out here that ABY itself has an explicit limit on circuit size and also give an example of a program that easily surpasses this bound? Also, hadnt ABY also said something about this? If so, we can mention this.}
To address this issue, we develop a technique called \emph{pipelining} that allows us to run aribitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of pipelining and prove the correctness and security of this transformation in \sectionref{pipe}.

\textbf{Baseline.} Finally, our framework \tool can serve as a meaningful baseline for future works on hand-crafted SMC protocols for specific functionalities such as \textsc{MiniONN} \cite{minionn}. 
Prior to our work, garbled circuit based two-party computation is cited as the most practical approach and used as the baseline for comparison of performance. But, it has been observed multiple times this approach does not even scale on realistic examples.

@@

\noindent\textbf{Related Work} \divya{I think we should say a few words here about the following: minionn, verilog paper, tasty, 
\cite{lambdaps,wysteria}

### 2017-10-13 OaklandSubmission/related.tex
edits and comments to Sec 1 and 2.
related

\divya{Related Work: writing some citations here to be used appropriately.}
\begin{enumerate}
\item Secure Computation of MIPS Machine Code https://eprint.iacr.org/2015/547
\item TASTY https://eprint.iacr.org/2010/365.pdf
\item ABY cites many papers on first page of intro for using a mix of HE and boolean MPC; but they didnt give much gain because HE is expensive

>>>>

\divya{Related Work: writing some citations here to be used appropriately.}
\begin{enumerate}
\item Secure Computation of MIPS Machine Code https://eprint.iacr.org/2015/547
\item TASTY https://eprint.iacr.org/2010/365.pdf. Does not have language; user has to know what parts in HE and what in Yao and writes something similar to ABY
\item ABY cites many papers on first page of intro for using a mix of HE and boolean MPC; but they didnt give much gain because HE is expensive
\nc{I will look into this and write.}
\item verilog, hardware tool chain paper http://encrypto.de/papers/DDKSSZ15.pdf
\item automatic choosing between HE and Yao https://eprint.iacr.org/2014/200.pdf 
I think this one still does not have a language; I don't know how to specify function
